Differentially Private Bayesian Inference

### 2018-06-19 main.tex
fix mistakes in notes

\section{Accuracy Analysis}
\subsection{Laplace Mechanism}
Fixing a data set $x$, we will sample noise $Lap_i = floor(Y)$ where $Y \sim Lap(\frac{2}{\epsilon})$. Since already had the accuracy bound based on the $l_1$ norm in Laplace mechanism as:
\begin{equation*}
Pr[|Y| \geq t] = e^{- \frac{t \epsilon}{2}}.
\end{equation*}

@@

\subsection{Exponential Mechanism with Global Sensitivity}
Also, from the \cite{dwork2014algorithmic}, we already had the accuracy bound of exponential mechanism with global sensitivity as:
\begin{equation*}
\underset{z \thicksim \hexpmech(x)}{Pr}[ \hlg(\bysinfer(x), z) \geq c] \leq  \frac{|R| \exp{(\frac{- \epsilon c}{2 \Delta_g}})}{|R_{OPT}|\exp{(\frac{- \epsilon OPT_{\hlg(\bysinfer(x), z)}(x)}{2 \Delta_g})}},
\end{equation*}
where $|R|$ is the size of the candidate set. Since $OPT_{\hlg(\bysinfer(x), z)}(x) = 0$ and $|R_{OPT}| = 1$, we have a simplified accuracy bound here $\underset{z \thicksim \hexpmech(x)}{Pr}[ \hlg(\bysinfer(x), z) \geq c] \leq |R| \exp{(\frac{- \epsilon c}{2 \Delta_g}}),$

\subsection{Exponential Mechanism with Smooth Sensitivity}
We explored three accuracy bound for our exponential mechanism.

@@

In order to be more efficiently, we design the second accuracy bound which is slightly looser than the first one:

@@

\begin{equation*}
\underset{z \thicksim \hexpmech(x)}{Pr}[ \hlg(\bysinfer(x), z) \geq c] \leq \ \frac{|R| \exp{(\frac{- \epsilon c}{S(x)}})}{N(n)},
\end{equation*}
where we replace the $NL_x$ with a value only related to the size of the data. We haven't figure out the formula of this $N(n)$.

In the three accuracy bounds, we will use the first one mostly in following analysis.

\section{Experimental Evaluations}
\subsection{Computation Efficiency}
The formula for computing the local sensitivity is presented in Sec. \ref{subsec_emls}:$\max\limits_{\{|x,y'| \leq 1; y'\in \mathcal{X}^n\}}\max\limits_{\{r\in R\}} \{\hlg(\bysinfer(x), r) - \hlg(\bysinfer(y'), r)|\}$ can be reduced to $\max\limits_{\{|x,y'| \leq 1;y'\in \mathcal{X}^n\}}\hlg(\bysinfer(x), \bysinfer(y'))|$ by applying the distance triangle property. i.e., the maximum value over $\max\limits_{r \in R}$ always happen when $r = \bysinfer(x)$ itself, where $\Delta_{l}u(x) = \max\limits_{\{|x,y'| \leq 1;y'\in \mathcal{X}^n\}} \{\hlg(\bysinfer(x), \bysinfer(x)) - \hlg(\bysinfer(y'), \bysinfer(x))|\} = \max\limits_{\{|x,y'| \leq 1;y'\in \mathcal{X}^n\}} \{\hlg(\bysinfer(y'), \bysinfer(x))|\}$. We also have some experiments for validating our proposal as in Fig. \ref{fig_efficiency}, where we calculate the $\max\limits_{\{|x,y'| \leq 1;y'\in \mathcal{X}^n\}}$ value for every candidate $r \in R$. It is shown that maximum value taken when  $r = \bysinfer(x)$.

@@

\subsection{Experimental Evaluations on Accuracy}
In this section, we do some experiments in order to study the accuracy property of these mechanisms, including the exponential mechanism with three kind of sensitivity and the Laplace mechanism.

@@

We first analyzed the accuracy based on the Hellinger distance. By repeating the experiments for 10000 times and plotting the accuracy after each execution, we got two groups of results under different parameters setting as in Fig. \ref{fig_beta_hellinger} and Fig. \ref{fig_dirichlet_hellinger}. X-axis is labeled with different mechanisms. We took four mechanisms in our experiments: our newly designed exponential mechanism with smooth sensitivity named ``ExpoMech of SS'', exponential mechanism with local sensitivity named `` ExpoMech of LS'', exponential mechanism with global sensitivity named `` ExpoMech of GS'' and Laplace mechanism named ``LaplaceMech''. Y-axis is the accuracy measured by Hellinger distance between output $r$ of each execution and the correct inference result $\bysinfer(x)$, $\hlg(r, \bysinfer(x))$.

@@

To have more experimental results, we then extended the $\betad$ to the $\dirichlet$ distribution as well as increased the data size, plotted in Fig. \ref{fig_dirichlet_hellinger}.

@@

\subsection{Evaluations on Accuracy Trade-off Between Laplace and Our Exponential Mechanism with Smooth Sensitivity}
\label{subsec_accuracy_tradeoff}
Based on accuracy study in Sec. \ref{subsec_accuracy_hellinger} and \ref{subsec_accuracy_l1}, we are going to have a further study on the relationship between Laplace mechanism and our exponential mechanism. We will do analysis both in theory and experiment based on accuracy bound and probability formula, and then study on some concrete cases.

@@

	\item However in Laplace mechanism, the probability of producing noise has little relevance with the size of the candidate set. In $m$ dimensional Dirichlet distribution, when the correct posterior distribution is $\dirichlet(\alpha_1, \alpha_2, \cdots, \alpha_m)$, we are adding Laplace noise in this way: $\dirichlet(\alpha_1 + Lap_1, \alpha_2 + Lap_2, \cdots, n - (\alpha_1 + Lap_1 + \alpha_{m-1} + Lap_{m-1}))$ where $Lap_i \sim Floor(Lap(\frac{2}{\epsilon}))$ are identical and independently. So we will have a list of noise $L_{noise} = \{|Lap_1|, |Lap_2|,\cdots ,|Lap_{m-1}|\}$ by taking the absolute value of every noise $|Lap_i|$. In order to get the probability of one candidate, we also need to have a set of noise $S_{noise}$ obtained from $L_{noise}$ by removing its duplicate values and a list $L_{noise/0}$ by removing the value 0 from $L_{noise}$. Then, the probabilities of outputting one candidate in Laplace mechanism can be computed by:

@@

	From analysis above, we can see the probabilities of output the good answers will not changed a lot as the size of the candidate set increasing. Specifically, we can easily have two upper bounds: $|S_{noise}| \leq (m-1)$ and $|L_{noise/0}| \leq (m-1)$. From the two upper bounds, we can have that the probabilities of outputting good answers are decreasing with speed upper bounded by $(m-1)! \times 2^{m-1}$. Since $n \gg 2$ and $m$ is usually smaller than $10$, it is easy to see that the decay speed $(m-1)! \times 2^{m-1}$ in Laplace mechanism is much more smaller than $n^{m-1}$ in our exponential mechanism. Moreover, when the steps are small, $0$ for example, $|S_{noise}| = |L_{noise/0}|  = 0$, which means the probability of correct answer will decrease very little no matter how large the candidate set is.

@@

		Here, there are only 5 kind of steps from correct answer. Our mechanism in the second column is clearly better than Laplace mechanism in the third column. When the candidates are close to correct answer (for example, $0, 1, 2$ steps from correct answer), our mechanism can output them with higher probabilities than Laplace mechanism. On the other hand, when candidates are far away from correct answer (for example, $3, 4$) steps), our mechanism can output them with lower probabilities.

@@

		This case shows that the Laplace mechanism do much better than our exponential mechanism significantly. These good answers with few steps from correct answer can be outputted with higher probabilities in Laplace mechanism than in our mechanism. Moreover, in our mechanism the bod answer and good answer have very similar outputting probabilities.

@@

\subsubsection{Experiment Analysis}
In this part, we will do some experiment analysis to study the accuracy trade-off between our exponential mechanism and Laplace mechanism. By computing the two mechanisms' discrete probabilities wrt. steps from correct answer. Then we got groups of discrete probabilities wrt. the steps (i.e., Hellinegr distance) from the correct answer, and plotted them. Under different settings, we got same results as in Fig. \ref{fig_theory_50_50}, \ref{fig_theory_20_20_20} and \ref{fig_theory_20_20_20_20}.

>>>>

\section{Accuracy Analysis}
\subsection{Laplace Mechanism}
Fixing a data set $x$, we will sample noise $Lap_i = floor(Y)$ where $Y \sim Lap(\frac{2}{\epsilon})$. Since already had the accuracy bound based on the $l_1$ norm in Laplace mechanism:
\begin{equation*}
Pr[|Y| \geq t] = e^{- \frac{t \epsilon}{2}}.
\end{equation*}

@@

\subsection{Exponential Mechanism with Global Sensitivity}
Also, according to \cite{dwork2014algorithmic}, we already had the accuracy bound of exponential mechanism with global sensitivity as:
\begin{equation*}
\underset{z \thicksim \hexpmech(x)}{Pr}[ \hlg(\bysinfer(x), z) \geq c] \leq  \frac{|R| \exp{(\frac{- \epsilon c}{2 \Delta_g}})}{|R_{OPT}|\exp{(\frac{- \epsilon OPT_{\hlg(\bysinfer(x), z)}(x)}{2 \Delta_g})}},
\end{equation*}
where $|R|$ is the size of the candidate set. Since $OPT_{\hlg(\bysinfer(x), z)}(x) = 0$ and $|R_{OPT}| = 1$, we simplified accuracy bound here $\underset{z \thicksim \hexpmech(x)}{Pr}[ \hlg(\bysinfer(x), z) \geq c] \leq |R| \exp{(\frac{- \epsilon c}{2 \Delta_g}}),$

\subsection{Exponential Mechanism with Smooth Sensitivity}
We explored three accuracy bounds for our exponential mechanism with smooth sensitivity.

@@

In order to be more efficient, we designed the second accuracy bound which is slightly looser than the first one:

@@

\begin{equation*}
\underset{z \thicksim \hexpmech(x)}{Pr}[ \hlg(\bysinfer(x), z) \geq c] \leq \ \frac{|R| \exp{(\frac{- \epsilon c}{S(x)}})}{N(n)},
\end{equation*}
where we replace the $NL_x$ with a value only related to the size of the data. However, we haven't figured out the formula of this $N(n)$.

Within the three accuracy bounds, we will mainly use the first one in following analysis.

\section{Experimental Evaluations}
\subsection{Computation Efficiency}
The formula for computing the local sensitivity presented in Sec. \ref{subsec_emls}:$\max\limits_{\{|x,y'| \leq 1; y'\in \mathcal{X}^n\}}\max\limits_{\{r\in R\}} \{\hlg(\bysinfer(x), r) - \hlg(\bysinfer(y'), r)|\}$ can be reduced to $\max\limits_{\{|x,y'| \leq 1;y'\in \mathcal{X}^n\}}\hlg(\bysinfer(x), \bysinfer(y'))|$ by applying the distance triangle property. i.e., the maximum value over $\max\limits_{r \in R}$ always happen when $r = \bysinfer(x)$ itself, where $\Delta_{l}u(x) = \max\limits_{\{|x,y'| \leq 1;y'\in \mathcal{X}^n\}} \{\hlg(\bysinfer(x), \bysinfer(x)) - \hlg(\bysinfer(y'), \bysinfer(x))|\} = \max\limits_{\{|x,y'| \leq 1;y'\in \mathcal{X}^n\}} \{\hlg(\bysinfer(y'), \bysinfer(x))|\}$. We also have some experiments for validating our proposal as in Fig. \ref{fig_efficiency}, where we calculate the $\max\limits_{\{|x,y'| \leq 1;y'\in \mathcal{X}^n\}}$ value for every candidate $r \in R$. It is shown that maximum value taken when  $r = \bysinfer(x)$.

@@

\subsection{Experimental Evaluations on Accuracy}
In this section, we do some experiments in order to study the accuracy property of these mechanisms, including the exponential mechanism with three kinds of sensitivity and the Laplace mechanism.

@@

We first analyzed the accuracy based on the Hellinger distance. By repeating the experiments for 10000 times and plotting the accuracy of each execution, we got two groups of results under different parameters setting as in Fig. \ref{fig_beta_hellinger} and Fig. \ref{fig_dirichlet_hellinger}. X-axis is labeled with different mechanisms. We took four mechanisms in our experiments: our newly designed exponential mechanism with smooth sensitivity named ``ExpoMech of SS'', exponential mechanism with local sensitivity named `` ExpoMech of LS'', exponential mechanism with global sensitivity named `` ExpoMech of GS'' and Laplace mechanism named ``LaplaceMech''. Y-axis is the accuracy measured by Hellinger distance between output $z$ of each execution and the correct inference result $\bysinfer(x)$, $\hlg(z, \bysinfer(x))$.

@@

To have more experimental results, we then extended the $\betad$ to the Dirichlet distribution $\dirichlet$ as well as increased the data size, plotted in Fig. \ref{fig_dirichlet_hellinger}.

@@

\subsection{Evaluations on Accuracy Trade-off Between Laplace and Our Exponential Mechanism with Smooth Sensitivity}
\label{subsec_accuracy_tradeoff}
Based on accuracy study in Sec. \ref{subsec_accuracy_hellinger} and \ref{subsec_accuracy_l1}, we are going to have a further study on the accuracy relationship between Laplace mechanism and our exponential mechanism. We will do analysis both in theory and experiment and do some concrete case studies.

@@

	\item However in Laplace mechanism, the probability of producing noise has little relevance with the size of the candidate set. In $m$ dimensional Dirichlet distribution, when the correct posterior distribution is $\dirichlet(\alpha_1, \alpha_2, \cdots, \alpha_m)$, we are adding Laplace noise in this way: $\dirichlet(\alpha_1 + Lap_1, \alpha_2 + Lap_2, \cdots, n - (\alpha_1 + Lap_1 + \alpha_{m-1} + Lap_{m-1}))$ where $Lap_i \sim Floor(Lap(\frac{2}{\epsilon}))$ are i.i.d. So we will have a list of noise $L_{noise} = \{|Lap_1|, |Lap_2|,\cdots ,|Lap_{m-1}|\}$ by taking the absolute value of each noise $|Lap_i|$. In order to get the probability of a single candidate, we also need to have the set of noises $S_{noise}$ obtained from $L_{noise}$ by removing its duplicate values and the list $L_{noise/0}$ by removing 0s from $L_{noise}$. Then, the probabilities of outputting a single candidate in Laplace mechanism can be obtained by:

@@

	From analysis above, we can see the probabilities of outputting the good answers will not change a lot as the size of the candidate set increasing. Specifically, we can easily have two upper bounds: $|S_{noise}| \leq (m-1)$ and $|L_{noise/0}| \leq (m-1)$. From the two upper bounds, we can see that the probabilities of outputting good answers are decreasing with speed upper bounded by $(m-1)! \times 2^{m-1}$. Since $n \gg 2$ and $m$ is usually smaller than $10$, it is easy to see that the decay speed $(m-1)! \times 2^{m-1}$ in Laplace mechanism is much more smaller than $n^{m-1}$ in our exponential mechanism. Moreover, when the steps are small, $0$ for example, $|S_{noise}| = |L_{noise/0}|  = 0$, which means the probability of correct answer will decrease very little no matter how large the candidate set is.

@@

		Here, there are only 5 kinds of steps from correct answer. Our mechanism in the second column is clearly better than Laplace mechanism in the third column. When the candidates are close to correct answer (for example, $0, 1, 2$ steps from correct answer), our mechanism can output them with higher probabilities than Laplace mechanism. On the other hand, when candidates are far away from correct answer (for example, $3, 4$ steps), our mechanism can output them with lower probabilities.

@@

		This case shows that the Laplace mechanism do much better than our exponential mechanism significantly. These good answers with few steps from correct answer can be outputted with higher probabilities in Laplace mechanism than in our mechanism. Moreover, in our mechanism the bad answers and good answers have very similar outputting probabilities.

@@

\subsubsection{Experiment Analysis}
In this part, we will do some experiment analysis to study the accuracy trade-off between our exponential mechanism and Laplace mechanism. By computing the two mechanisms' discrete probabilities wrt. steps (i.e., Hellinegr distance) from correct answer under different settings, we got groups of results as in Fig. \ref{fig_theory_50_50}, \ref{fig_theory_20_20_20} and \ref{fig_theory_20_20_20_20}.
